---
title: "COVID19 in THAILAND"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## What is this? 

I have completed a data scientist with R course, and want to practice applying recently-gained knowledge on COVID19 situation in Thailand. 

```{r}
library("dplyr")
library("ggplot2")
```
## Importing the data with the below code chunk
```{r}
library(readr)
covid <- read_csv("https://raw.githubusercontent.com/RamiKrispin/coronavirus/master/csv/coronavirus.csv")
covid
```

## Exploring the data
The structure and summary of covid dataset are shown below. 
```{r}
str(covid)
summary(covid)
```

## Thailand dataset
First, check if there is any observation from Thailand. 
```{r}
any(covid$country=="Thailand")
```

Next, we can filter for only confirmed cases in Thailand, and explore them. 
```{r}
covid_th <- covid %>%
  filter(country == "Thailand",type=="confirmed")
summary(covid_th)
```

From the above summary, I notice that there is one or more cases with negative value, which is impossible. Thus, I will filter those observations out and make a cases vs date plot. 
```{r}
covid_th <- covid_th %>%
  filter(cases >= 0) %>%
  select(date,country,cases)
summary(covid_th)
ggplot(covid_th,aes(x=date,y=cases)) +
  geom_line() +
  ylab("Confirmed cases in Thailand")
```

Now, let's add a new column for 'cumulative cases', plot a line plot for cum_cases vs date and fit a linear regression model with the below code chunk.
```{r}
covid_th_cum <- covid_th %>%
  mutate(cum_cases = cumsum(cases))
summary(covid_th_cum)
ggplot(covid_th_cum, aes(x=date,y=cum_cases)) +
  geom_line() +
  geom_smooth(method="lm",se=FALSE)
```

Since the end of 2020, cases in Thailand skyrocketed. 
Let's focus only on data since December.
```{r}
covid_th_dec <- covid_th_cum %>%
  filter(date >= "2020-12-01")
ggplot(covid_th_dec, aes(x=date,y=cum_cases)) +
  geom_line() +
  geom_smooth(method="lm",se=FALSE) 
```

Let's examine more on the peak period.
```{r}
peak <- covid_th_dec %>%
  filter(cases == max(cases))
peak
```

On January 29, Thailand has reached its peak of 1732 due to Samutsakhon cluster. 
```{r}
ggplot(covid_th_dec, aes(x=date,y=cum_cases)) +
  geom_line() +
  geom_smooth(method="lm",se=FALSE) +
  geom_vline(aes(xintercept=date),data=peak,linetype="dashed") +
  geom_text(aes(x=date,label="Samutsakhon cluster"),data=peak, y=30000)
```

Let's build a linear model from 'covid_th_dec' data set to see the trend. 
```{r}
covid_model <- lm(cum_cases~date, data=covid_th_dec)
summary(covid_model)
```

The model seems to explain the situation since December 2020 well, but I hope that this upward trend will not continue. 

## Data source 
https://github.com/RamiKrispin/coronavirus

THANK YOU :) 


