---
title: "Holidays_070721"
author: "Chanya"
date: "7/7/2021"
output: html_document
---

```{r setup, include=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
```

## Installing packages and reading a dataset into R
data source : [tidytuesday repository](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-06/readme.md)
```{r install R packages, message=FALSE, warning=FALSE, include=FALSE}
packages <- c("tidyverse","forcats","gapminder","ggthemes","wesanderson")
lapply(packages, install.packages)
```
```{r install Rcpp?, message=FALSE, warning=FALSE, include=FALSE}
install.packages("Rcpp")
```
### Loading Packages into R 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(forcats)
library(gapminder)
library(ggthemes)
library(wesanderson)
```

### Loading dataset from Github
```{r load dataset, warning=FALSE, include=FALSE}
holidays <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-06/holidays.csv")
```

```{r view dataset}
view(holidays)
glimpse(holidays)
summary(holidays)
```

## Questioning
After viewing the data, I would like to further answer two questions
1. Which countries do not celebrate Independence Day? 
2. Which countries colonized the most? 

## Before finding the answers, data wrangling! 
Big thanks to : [Julianna Calabrese](https://github.com/jrcalabrese/TidyTuesday/blob/main/2021_week28/independence.Rmd)
```{r}
holidays_2 <- holidays %>% 
  select(country,date_parsed,independence_from,year) %>%
    mutate(independence_from = 
           recode_factor(independence_from, "Russian Soviet Federative Socialist Republic" = "Soviet Union")) %>% 
  mutate(independence_from = 
           recode_factor(independence_from, "Russian Soviet Federative Socialist Republic and German Empire" = "Soviet Union")) %>% 
  mutate(independence_from = 
           recode_factor(independence_from, "Spanish Empire" = "Spain")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "United Kingdom of Great Britain" = "United Kingdom")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "Kingdom of Great Britain" = "United Kingdom")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "United Kingdom of Great Britain and Ireland" = "United Kingdom")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "United Kingdom of Portugal, Brazil and the Algarves" = "Portugal")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "United Kingdom and the British Mandate for Palestine" = "United Kingdom")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "SFR Yugoslavia" = "Yugoslavia")) %>% 
  mutate(independence_from = 
           recode_factor(independence_from, "Socialist Federal Republic of Yugoslavia" = "Yugoslavia")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "Empire of Japan and France" = "Empire of Japan")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "Spanish Empire[72]" = "Spain")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "Soviet Union[80]" = "Soviet Union")) %>%
  mutate(independence_from = 
           recode_factor(independence_from, "Soviet Union[55]" = "Soviet Union")) %>%
  mutate(across(independence_from, fct_explicit_na, "never or not celebrated"))
```

```{r install skimr}
install.packages("skimr")
```
```{r}
library(skimr)
skim(holidays_2)
```


### Question 1 : Out of 195 countries, which never celebrate Independence Day? 
```{r}
question_1 <- holidays_2 %>%
  filter(independence_from == "never or not celebrated")
question_1$country
```
There are 35 out of 195 countries which do not celebrate Independence Day. 
Some of the countries have never been colonized while some were colonized but did not celebrate the Independence Day.

### Question 2 : Which countries colonized the most? 
```{r}
ggplot(holidays_2, aes(x=fct_infreq(independence_from))) +
  geom_bar(fill="sky blue") +
  coord_flip() 
colonizers <- holidays_2 %>%
  group_by(independence_from) %>%
  count() %>%
  arrange(desc(n)) 
head(colonizers)
ggsave("colonizers.png", height=8, width=8)
```

### Mapping data
```{r}
mapdata <- map_data("world") %>%
  filter(!(region=="Antarctica")) %>%
  filter(!(region=="Greenland")) %>%
  filter(!(region=="French Southern and Antarctic Lands")) %>% 
  mutate(region = recode(region,
                         USA="United States",
                         UK="United Kingdom"))
holidays_2 %>% 
  mutate(independence_from = fct_lump(independence_from, n=7)) %>%
  ggplot() + 
  geom_map(dat = mapdata, map = mapdata, aes(map_id=region), fill="#E86F00", color=NA) +
  geom_map(aes(map_id=country, fill=independence_from), map=mapdata) + 
  expand_limits(x = mapdata$long, y = mapdata$lat) +
  coord_map(projection = "gilbert", xlim = c(-180, 180)) +  #mollweide
  ggthemes::theme_map() +
  theme(
        text=element_text(family="Gill Sans"),   
        plot.title = element_text(size=20, hjust = 0.5),
        plot.background = element_rect(fill = "white", color=NA),
        legend.position = "top",
        legend.justification = "center",
        legend.background=element_blank(),
        legend.key = element_rect(colour = NA, fill = NA), 
        legend.box.background = element_blank(),
        legend.text=element_text(size=rel(2))) +
  scale_fill_manual(values = wes_palette("FantasticFox1", 8, type = "continuous"),
                      na.value="#E86F00", na.translate=F) +
  guides(fill=guide_legend(title="", ncol=3)) +
  ggtitle("Colonization in World Map") +
  labs(caption = "Thank you @jrosecalabrese for the code") +
  theme(plot.caption= element_text(size=16, hjust=1))
ggsave("independence_map.png", height=8, width=8)
```
## Final Words

This is my first time mapping in R (and also my first time analyzing #TidyTuesday data. I would not have finished it without the comprehensive and reproducible code from [Julianna Calabrese](https://github.com/jrcalabrese/TidyTuesday/blob/main/2021_week28/independence.Rmd). I have learned a lot, and I am inspired to explore further into the related packages. 


